\chapter{Car Park Ventilation}

\newthought{The Car Park ventilation system} is not expected to be completed by the \deadline. However, we expect to have large sections of it at an advance stage. Current delays revolve around remaining Engineering issues and the finalization of a CFD\sidenote{Computational Fluid Dynamics} simulation study, that is necessary to prove the systems offered and obtain final approval from the Consultants. We are also expecting a major EI, affecting a number of these systems in the Basements. \sidenote{This has now been received (17th August)}


\section{Constraints}
Constraints revolve around the detailing of the Car Park ventilation,  main fans, location etc. It is likely that there will be a need to order new equipment, both Jet fans as well as Extract fans. The condition of some of the fans is suspect and remedial works might be necessary. Sound attenuators have not been ordered and can take a while.

The Jet Fan system employed needs to be validated via CFD studies. These can only be completed when the full design is complete. At the moment we have been informed that this is on hold.

This is also affecting the \texttt{CO} System, which is dependent on the location of the Jet Fans. In addition all the MCC Panels have still not been finalized for the same reason.

Co-ordination for all these equipment and ductwork is difficult as no primary co-ordination has been done by the Engineer. Headroom restrictions prohibit an easy and quick installation.

Based on these constraints and the delivery of balance of equipement, we estimate that the earliest date for completion of these systems will be the end of December. \out{Car Park Ventilation}{30 Dec 2010}
\out{Car Park CO System}{30 Dec 2010}

\section{Recommended action}

An adequate EOT must be sought as well as necessary compensation, although the contention of HEE is that all these additional changes were due to the re-design of the structure by HEE that introduced space constraints.