\chapter{Civil Defence Approval}
\parindent1em
\label{civildefence}
Civil Defence Inspections can only take place when the Building Operations have been completed, when the full Fire Fighting,  Fire Alarm, Staircase Pressurization and Smoke Exhaust systems have been completed tested and commissioned. We expect that this will only be possible at the earliest by end April  2013. However, we will re-evaluate these dates once the works progress a bit further. 


The Qatar Civil Defence Department if approached can unofficially inspect the works earlier in order to identify problem areas earlier. However, at this stage it is bound to catch rather known problems than unknown problems.

The Civil Defence related sections have been discussed under separate headings and will not be repeated here. See \tref{cdd} for status and details.


\begin{table}[h]
\begin{tabular}{lr}
\toprule
\textbf{Description}	 &\textbf{Qty}\\
\midrule 	 
\textbf{Fire Fighting System}	 &\\
Sprinkler Points	    &26,078\\
Fire Hose Cabinets	    &457 \\
Zone Control Valves	    &393 \\
Pressure Reducing Valves	 &288 \\
Breeching Inlets	        &3\\ 
Fire Hydrants	            &13\\ 
OS\&Y Valves	               &86\\ 
\textbf{Alarm Check Valves}	              &18 \\
Check Valves / Non Return Valves &18 \\
Fire Extinguishers Dry Powder	 &691 \\
Fire Extinguishers CO2	           &457 \\
Fire Pumps	                     &12 \\
Jockey Pumps	                     &6 \\
\midrule 	 
\textbf{Fire Alarm System}	 &\\
Smoke \& Heat Detectors	 &7,573 \\
Monitor / Control Modules	       &2,252 \\
Sounders / Speakers / Voice Evacuation	   &2,630 \\
Main Fire Alarm Control Panel	         &9 \\
Conventional Fire Alarm Panel	        &16 \\
Voice Evacuation Panel	                  &9 \\
\midrule 
\textbf{FM200 System}	 &\\
Fire Extinguisher Control Panel	&36 \\
FM200 Cylinder with Agent	            &38 \\
\midrule 	 
\textbf{Foam System}	 &\\
Deluge Valve with complete trimming	 &2 \\
Bladder Tank	                        &2 \\
Foam Chemical	                   &100 Gal\\
\bottomrule
\end{tabular}
\caption{Items comprising the Fire Protection System}
\label{fireitems}
\end{table}

\tref{fireitems} lists all the devices related to Fire Life Safety code requirements and indicates clearly the extend of the challenge to complete the installation and commissioning within the stipulated time. Terminal devices are still to be installed in Merweb and a great number of them are still to be delivered. Of special concern are the large number of devices related to the Fire Alarm system (approximately 13,000) which are prone to errors and false alarms.




\medskip

\captionof{table}{Summary CDD requirements.}
\label{cdd}
{\small\RaggedRight
\begin{longtable}{p{2.3cm}p{4.2cm}p{4.2cm}}

\toprule
Fire Protection    &Firefighting system.  & Substantially ready.\\
    &Fire suppression FM~200 system. & 65\%\\
	&Fire alarm \& voice evacuation system. & ongoing\\
	&Fire alarm control rooms. & 75\%\\
	&Fire Water tanks & \Danger Expected Completion 20 Mar 2013 \\
	&Evacuation Map & HLG Scope\\
	&FA Matrix & Submitted\\
	&Life Safety \& fire protection cause and 
         effect report & \ch\\
	&Function \& Sequence of operation & On-going\\
\midrule

HVAC	&Staircase Pressurization System & Rotana, Shangrila tested, Merweb 15.03.2013. Retesting necessary on other two.\\
	&ECUs, SEF, EAF, AHU, FAF, ECU, SMD, FD etc… &\\
	&Car Park Ventilation & See \S\ref{carparkventilation}\\
	&Function \& sequence of operation &\\
\midrule


Electrical	&Exit \& emergency lights. &\\
	&Power Diesel generator \& ATS. &\\
	&DG Tanks. &\\
	&Access control system.  &\\
	&CPMS. &\\
	&UPS system. & See \refs{ups}\\
	&Lift sequence of operation &\\
\midrule

Documents	&Drawings &\\
	&Method Statements &\ch \\
	&Sequence of operation &\ch \\
	&Products certificates &\ch \\
	&T\&C reports, &\\
	&Undertaking letter to CDD &\\
	&Certificate of HLG \& NAFFCO &\\
        & Certificate Al-Misnad              &\ch 9 Mar 2013\\
	&MEP Function \& sequence of operation manual/Report, Interface \& Integrity reports &ongoing\\
	&Stamped \& approved Shop Drawing &\ch \\
\bottomrule
\end{longtable}
}

\section{Civil Defence Inspection Checklist base on Phase II Inspection}

Comments that need action based on Phase II inspection.

\input{./sections/cdd-issues}





