\chapter{Construction}

Our aim is to hit the ground running and to minimize risks of overruns and over costs. At its heart our strategy is based on the following two principles.

\begin{enumerate}
\item Once an activity is completed, all constraints for starting the next activity should be removed. 
\item Never, ever delay other parties. We would re-prioritize if necessary rather than delay other parties.
\item No activity to be started, unless there are shop drawings drawings. Many a time we try to save time by pro-actively starting activities, however any upfront gains in time come back and bite us later and we end spending more time.
\item Do the job right the first time.
\end{enumerate}

\section{Mobilization}

\begin{enumerate}
\item Offices.
\item Document Control.
\item Computers.
\item Adequate Shelving.
\item Tools and Equipment.
\item Worskhop.
\end{enumerate}

\section{Start-up Documentation}

\begin{enumerate}
\item Safety
\item Quality Assurance
\item Registers
\item 
\item 
\end{enumerate}

\section{Milestones}

The following milestones need to be established.

\begin{enumerate}
\item Information cut-off date.
\item Mock-ups (no need to make them in-situ).
\item Power-on.
\item Wild Air.
\item Civil Defence.
\item Other Statutory.
\end{enumerate}

\begin{table}
\begin{tabular}{lp{3.5cm}}
\toprule
Item                               & Remarks \\
\midrule
Hotel Operator Requirement Manuals & Essential for design audit. \\
\hfill Westin &\\
\ZZ "W"      &\\
St. George & \\
IFC Drawings & \\
Structural Drawings & \\
Ceiling Layouts  &\\
Furniture Layouts &\\

\end{tabular}
\caption{Information Necessary for Completion of Shop Drawings and for Fast track Construction.}
\end{table}


















  





\section{Engineering Works Sequence}

\section{}













