\chapter{Drainage System}

\newthought{The Drainage System is already at an advanced stage}. Work that could be completed has been completed, especially in the Podia. In the Towers, Rotana and Shangrila are not expected to present a problem. Areas that are currently incomplete are second and third fix activities
in all public washrooms and main kitchens. For these areas information is still oustanding and or the Main Contractor's works have not been completed. 

\newthought{Drainage Planrooms} such as the Grey Water Treatment Plant is substantially completed in terms of Mechanical Works and the balance works, including electrical works are expected to be completed by end of August.

From a systems point of view our aim is to be able to pour water at the highest point
in the Tower and see it flowing into the Municipal Drain or the Grey Water Treatment Plant etc.
as soon as possible. This has been partially achieved during wild air, but has also exposed areas in Towers where risers have been erroneously reported as completed.

The installation can be divided into the following broad sections

	\begin{center}
           \begin{table} 
	    \begin{tabular}{ll}
	      \toprule
	      Plantroom   &  Milestone Date  \\
	      \midrule
	      Flushing/Grey Water       &    30 May 2013  \\
	      Rainwater System      &    30 May 2013  \\
	      Sump Pits    &    \ch  \\
	     Condensate Drains &\ch\\
	     External Works &\ch \\
	     Sanitary Fixtures installation &31 May 2013 \\ 
	      \bottomrule
	    \end{tabular}
             \caption{Organization of drainage activities}
             \end{table}
          \end{center}


Considerable rectification works are ongoing in Shangrila.


A detailed schedule of constraints is available.



