\chapter{Electrical Installation}
\label{ch:electrical}\index{Electrical Installation}

\newthought{The majority of the electrical systems} have been completed. However, certain activities such as final fix of lights are still being carried out. \sidenote{These are dependent on Fit-out Contractor completing wall cladding and ceilings on time.} 

\section{List of Services}
Under this section of the report the following systems are discussed.

\bgroup
\small
\label{chap:listofservices}

\begin{longtable}{llllp{4.2cm}}
%\begin{tabular}{llll}
\toprule
Ref	&Package	&Commiss.	&Perc. & Commissioning Status\\
     &         &Entity    &Compl.\\
\midrule
2.00	&\textbf{Electrical}		&& 80\% complete\\
2.01	&Standby Generators	&Specialist&80\% & Started on flushing for cooling towers. Commercial issues to be sorted out. (See \refs{generators}.)\\	
2.02	&Medium Voltage System	&HS&100\% & Good progress all over. Panels missing and on order.\\	
2.03	&Low Voltage System		&HS&80\% & Started and being commissioning progressively.\\
2.04	&Earthing \& Lightning Protection &HS&80\% &earthing mostly completed. Lightning protection, missing parts arrived and installed. \\		
2.05	&Lighting \& Emergency Lighting  &HS&75\% & Where possible started. Fit-out needs to be completed in a few areas.\\		
2.06	&Aircraft Warning System &HS&80\% & Ready. Supplier requested to visit and commission. \\		
2.07	&UPS System	&Specialist& 75\% & \\	
2.08  &Power Factor  &Specialist &100\% & Completed.\\
\midrule
\end{longtable}
\egroup



\section{Current Status}
\subsection{MCB SMDBs MCC Panels}
Commissioning of MCB, SMDBs and MCC panels is expected to be completed by 31 Mar 2013. We expect to complete all related snagging and closure of issues with the Engineer within 30-40 days after that.

%\begin{table}[htbp]
%\begin{tabular}{lllp{4.5cm}}
%\toprule
%Item &Detail &Floor  & Remarks\\
%
%\bottomrule
%\end{tabular}
%\caption{Final Snag List Electrical, Rotana}
%\end{table}




\subsection{Earthing \& Lightning Protection}

\begin{table}[h]
{\RaggedRight
\begin{tabular}{lp{3cm}lp{3cm}}
\toprule
Item &Detail &T\&C & Remarks\\
\midrule
1    & Rotana & \checkmark  & \\
2    & Shangrila & \checkmark & \\
3    & Merweb & \checkmark & \\ 
4    & Overall earthing resistance measurement & x & 13.0.2.13\\  
\bottomrule
\end{tabular}
\caption{Earthing Testing and Commissioning}
}
\end{table}

\begin{table}[h]
{\RaggedRight
\begin{tabular}{lllll}
\toprule
Item &Detail &Installation &T\&C &Milestone\\
\midrule
1    & Rotana         & 90\%  & & \\
2    & Shangrila      & 100\% & &\\
3    & Merweb         & 100\% & &\\   
\bottomrule
\end{tabular}
\caption{Lightning Protection}
}
\end{table}

\subsection{Exit Signage}
Exit signage first and second fix installations have been
completed and inspected. 

\setcounter{step}{0}
\begin{longtable}{llllp{3.8cm}}
\toprule
S/No &Level &Final Fix  & T\&C & Remarks\\
\midrule
\inc &7     &\checkmark       &      &        \\ 
\inc &6     &\checkmark       &      &       \\
\inc &5     &\checkmark       &      & Remaining areas are in current contractor offices.       \\
\inc &4     &\checkmark       &      &Remaining works are in stores and offices.       \\
\inc &3     &\checkmark       &      &Remaining works in stores and offices       \\
\inc &2     &\checkmark       &      &Teatro restaurant, Teatro kitchen, Meeting rooms (Dragoni constraints).  \\
\inc &1     &\checkmark       &      &       \\
\inc &GR    &\checkmark      &      & Dragoni       \\
\inc &B1    &\checkmark       &      &     \\
\inc &B2    &\checkmark       &      &       \\
\inc &B3    &\checkmark      &      &       \\
\bottomrule
\caption{Exit Signage status.}
\end{longtable}

\subsection{Constraints}





\begin{table}[h]
{\RaggedRight
\begin{tabular}{lllll}
\toprule
Item &Detail &Installation &T\&C &Milestone\\
\midrule
1    & Rotana         & 90\%  & & \\
2    & Shangrila      & 90\% & &\\
3    & Merweb         & 90\% & &\\   
\bottomrule
\end{tabular}
\caption{Emergency Lighting}
}
\end{table}

Table~\ref{tbl:ROpanels} shows the current and projected dates for completion of T\&C and paperwork for this service.

\input{./sections/RO-MCC}
\vspace*{2cm}


\input{./sections/SL-MCC}
\vspace*{2cm}

\input{./sections/MW-MCC}

\section{Electrical Final Fix Materials}

Final fix activities are currently being delayed due to Finishing Contractor's activities. 
A number of final fix materials are still outstanding, these are listed in \tref{ELfinalfix}. 
\bigskip

{\small\RaggedRight
\captionof{table}{Pending final fix materials.}
\label{ELfinalfix}
\resetinc

\begin{longtable}{lllllp{3cm}}
\toprule
S/no & PO & Detail &Supplier & ETA  & Status\\
\midrule
\inc &EL-0219 & Wiring accessories SL & Carporal & Unknown &\Danger \\
\inc &EL-0327 & Wiring accessories    & Carporal & Unknown & \Danger affects VVIP rooms Rotana\\
\inc &EL-0386 & Wiring accessories SL & Carporal & 1 Mar 2013 & \\
\inc &EL-0387 & Wiring accessories SL & Carporal & 1 Mar 2013 &\\
\inc &EL-0368 & Media Hub Merweb      & Carporal & Unknown    &\Danger\\
\inc &EL-0408 & Media Hub             & Carporal & Unknown    &\Danger\\
\midrule
\inc &EL-0425 & Media Hub cables MW   & Advance Business & Unknown    &\Danger\\

\midrule
\inc &EL-0354 & MK Accessories       & Electrotrade & 3 Mar 2013\\
\inc &EL-0356 & MK Accessories       & Electrotrade & 3 Mar 2013\\
\inc &EL-0354 & MK Accessories       & Electrotrade & 3 Mar 2013\\
\inc &EL-0385 & MK Accessories       & Electrotrade & 5 Mar 2013\\
\inc &EL-0407 & MK Accessories       & Electrotrade & 5 Mar 2013\\
\inc &EL-0424 & MK Accessories       & Electrotrade & 5 Mar 2013\\
\inc &EL-0405-1  & Floor boxes       & Electrotrade & 5 Mar 2013\\
\inc &EL-0430    & Face plate        & Electrotrade & 5 Mar 2013\\
\bottomrule
\end{longtable}
}











