\chapter{Electrical Installation}
\label{ch:electrical}\index{Electrical Installation}

\newthought{The majority of the electrical systems} can be completed before the \deadline. However, it is not expected that third fix activities will be completed in Towers or Podia. \sidenote{These are dependent on Fit-out Contractor completing wall cladding and ceilings on time. In areas, where ceilings are not a constraint, such as Car Parking areas and Plantrooms light fittings are currently being installed.} We expect by the \deadline~that the building will have permanent power and that we will provide power to all major plantrooms. We also expect that lights will be on where the activities of the Fit-out Contractor permit to do so.

\section{Current Status}
Currently work in all Substations is almost completed and we expect Kahraama connections to follow the details outlined in the section for power on (see page \pageref{ch:kahraama}). Deliveries of panels has improved - although there are delays in some of the dates promised - and we expect Verger to be able to deliver all panels within a reasonable deviation from the dates agreed.

Cable pulling has slowed down, primarily due to a commercial dispute after the Cable Pulling Subcontractor (MBK) caused damages to a number of cables. Specon recommended a second Subcontractor (Markwell), but this suggestion was turned down by HEE. This issue is currently delaying power-on.

Missing busduct pieces have been delivered and the busduct installations are currently being completed. We expect that these will be inspected withing the first two weeks of August in order to allow us to partially power on the Building, when power becomes available. 

Good progress has been made on Towers, especially with conduiting in walls.

A detailed program for power-on is available and too long to include here.

Remaining material and engineering issues are not expected to have any major impact on completion dates. However, the ever changing Mechanical requirements are expected to cause some co-ordination issues.

\section{Key Milestone Dates}

