\chapter{External Works}

\newthought{MEP} remaining external works, are primarily electrical. Lights, where available have been
installed. Earthing pits, where they could not be reached due to temporary installations covering the areas
are being progressed, immediately as they are made available.

A small team of Electrical technicians, is expected to remain occupied on external works, until the end of February 2011, when we expect the works to have been completed.

\section{Remaining works}

\begin{table*}
\RaggedRight
\begin{tabular}{lp{3.5cm}p{3.5cm}}
\toprule
Sn &Activity &Remarks\\
\midrule
1  & Completion of light fittings and cabling &\\
2  & Completion of earthing system & \\
3  & Water meter installation&\\
4  & Condensing units for Qtel rooms\\
\bottomrule
\end{tabular}
\end{table*}

\section{Constraints to Complete the works}
\subsection{RFIs}
\subsection{EIs}
\subsection{Design Issues}
\subsection{Material Issues}
\subsection{Builder's Works Requisitions}
\subsection{Human Resources}
The area is adequately manned with the necessary man-power.


\section{Work Inspections}

The physical installations have been submitted via WIR. Any snags on WIRs, have been summarized and 
issued as snag-lists.

The following WIRs remain to be submitted. They are expected to be submitted as follows:

\section{Pre-commissioning}

Pre-commissioning activities relate to switch-on of the lights in the external areas. These are expected to follow completion of the physical works on the 15th February 2011.

\section{Commissioning}

Commissioning is expected to follow pre-commissioning and be completed by the end of February 2011.











