\chapter{Gas Installations}
\begin{update}
\centerline{\textbf{Update 26 April 2013}}
All physical works\footnote{With the exception of minor items in Dragoni's areas. These are to be completed as soon as Civil request are completed by Dragoni.}, including Engineer's Instructions are on track to be completed by 30 April with the exception of the additional sensors and cabling at the tank farm area (to be completed by 10 May 2013). WIRs are currently issued for the works and for testing. Final commissioning can only take place once gas is available on site. According to new \texttt{WOQOD} regulations this can only take place after the Civil Defence Inspection.

Electrical works are to be completed before the 10 May 2013.

Closure of paper work for Mechanical and Electrical WIRs is expected to be completed before the 15 May 2013, subject to a reasonable response time from the Engineer.
\end{update}


\begin{update}
\centerline{\textbf{Update 13 Mar 2013}}
So far more or less on track. Gasco remobilized to site and expected to complete the works by end March with the exception of EI-008a. Section of pipework on Level-5 delayed by drawing approval. Panels
have been installed in Fire Control Rooms for interfacing with Fire Alarm.
\end{update}

\newthought{The mechanical part of physical works} for the Gas Installations have been mostly completed with the exception of the Gas Meters which are currently being installed---where possible. On the electrical side final devices have not been installed. 

\section{Plan to completion}

We have met with Gasco and who will be supporting their site team with further technicians in order to complete the works by the 10 Apr 2013 (including Testing \& Commissioning) of the Electrical systems and final pressure testing of the mechanical systems. It is envisaged that Gasco will provide adequate personnel to
work in all three Towers in parallel.

Finals switch-on can only take place after Civil Defence approval.

Sign-offs and WIRs have not been submitted for Electrical works.
\vspace*{1.5cm}

\subsection{Mechanical}
\resetinc
\captionof{table}{Rotana Gas Installations, mechanical activities status.}
{\small \RaggedRight
\begin{longtable}{l l l ll p{3.5cm}}
\toprule
S/no.    & Level    & Area          & Inst. & \WIR & Remarks  \\ 
\midrule
%\inc      & L-24     & Restaurant  & & & 07 Mar 2013\\
\inc      & L-7       & Swim. Pool kitchen   &\ch &\ch  &15 Mar 2013\\
\inc      & L-2       & Teatro   &\hl{\ch}  &\ch  &13 Mar 2013\\
\inc      &             & EI-008a           &\hl{\ch} &\ch &30 Mar 2013\\
                          
\inc      &L-1        & All Day Rest..   &  &\ch &\hl{RFI Issued} 19 Mar 2013\\
\inc           &       & Lebanese  Rest.     &\hl{\ch} &\ch &22 Mar 2013\\
\inc           &       & Boston Bar.  &\ch &\ch  &25 Mar 2013\\
                            
\inc      &GF         & Banquet Kitchen   &\ch  &\ch  &27 Mar 2013\\

\inc      &B1         & Main Kitchen  &\ch &\ch &10 Mar 2013\\
\inc      &B3         & Boiler Plant room &\ch &\ch&\\
\bottomrule
\end{longtable}



\captionof{table}{Shangrila Gas Installations, mechanical activities status.}
{\small \RaggedRight
\begin{longtable}{l l l ll p{3.5cm}}
\toprule
S/no.    & Level    & Area          & Inst. & \WIR & Remarks  \\ 
\midrule
\inc      & L-42     & Chinese Rest.  &\ch & \ch&12 Mar 2013\\
\inc      & L-7       & Swim. Pool kitchen   &\ch &\ch  &30 Mar 2013\\
\inc      & L-2       & All Day Rest.   &\ch  &\ch &20 Mar 2013\\
\inc      &L-1        & Argentina Rest.   &\ch  &\ch &14 Mar 2013\\
           &            & Seafood  Rest.     &\ch  &\ch &16 Mar 2013\\
           &            & Teppanyaki Rest.  &\ch  &\ch &18 Mar 2013\\
                            
\inc      &GF         & Banquet Kitchen   &\ch   &\hl{\ch} &\\
\inc      &B1         & Main Kitchen  &\ch  &\hl{\ch} &\\
           &             & Small Kitchen &\ch    &\ch&10 Mar 2013\\
           &             & Staff canteen  &  &\hl{\ch}&\\
\inc      &B3         & Boiler Plant room &\ch &\ch &\\
\bottomrule
\end{longtable}
}

\captionof{table}{Merweb Gas Installations, mechanical activities status.}
{\small \RaggedRight
\begin{longtable}{l l l ll p{3.5cm}}
\toprule
S/no.    & Level    & Area          & Inst. & \WIR & Remarks  \\ 
\midrule
\inc      & L-3       & All Day Rest.   &\ch  &\ch &\\
\inc      &L-1        & Restaurant.   &\ch  &\ch &\\
\inc      &GF         & Banquet Kitchen   &\ch  &\ch &\\
\inc      &B1         & Main Kitchen  &\ch &\ch &\\
\inc      &B3         & Boiler Plant room &\ch &\ch &\\
\bottomrule
\end{longtable}

%%%
\subsection{Electrical}
Dates for electrical will be set on the next issue of the report.

\resetinc
\captionof{table}{Rotana Gas Installations, electrical activities status.}
{\small \RaggedRight
\begin{longtable}{l l l ll p{3.5cm}}
\toprule
S/no.    & Level    & Area          & Inst. & \WIR & Remarks  \\ 
\midrule
\inc      & L-24     & Restaurant  &\ch & &\fire\\
\inc      & L-7       & Swim. Pool kitchen   &\ch  &  &\fire\\
\inc      & L-2       & Teatro   &\ch   & &\fire\\
                          
\inc      &L-1        & All Day Rest.   &\ch   & &\fire\\
\inc           &            & Lebanese  Rest.     &\ch  & &\fire\\
\inc           &            & Boston Bar.  &\ch  & &\fire\\
                            
\inc      &GF         & Banquet Kitchen   &\ch   & &\fire\\
           &GF         & FC Center            &\hl{\ch} & &\fire\\
\inc      &B1         & Main Kitchen  &\ch  & &\fire\\
\inc      &B3         & Boiler Plant room &\ch  &&\fire\\
\bottomrule
\end{longtable}



\captionof{table}{Shangrila Gas Installations, electrical activities status.}
{\small \RaggedRight
\begin{longtable}{l l l ll p{3.5cm}}
\toprule
S/no.    & Level    & Area          & Inst. & \WIR & Remarks  \\ 
\midrule
\inc      & L-42     & Chinese Rest.  & & &\fire\\
\inc      & L-7       & Swim. Pool kitchen   & &  &\fire\\
\inc      & L-2       & All Day Rest.   &  & &\fire\\
\inc      &L-1        & Argentina Rest.   &  & &\fire\\
           &            & Seafood  Rest.     & & &\fire\\
           &            & Teppanyaki Rest.  & & &\fire\\
                            
\inc      &GF         & Banquet Kitchen   &  & &\fire\\
\inc      &B1         & Main Kitchen  & & &\fire\\
           &             & Small Kitchen &   &&\fire\\
           &             & Staff canteen  &  &&\fire\\
\inc      &B3         & Boiler Plant room & &&\fire\\
\bottomrule
\end{longtable}
}

\captionof{table}{Merweb Gas Installations, electrical activities status.}
{\small \RaggedRight
\begin{longtable}{l l l ll p{3.5cm}}
\toprule
S/no.    & Level    & Area          & Inst. & \WIR & Remarks  \\ 
\midrule
\inc      & L-3       & All Day Rest.   &  & &\fire\\
\inc      &L-1        & Restaurant.   &  & &\fire\\
\inc      &GF         & Banquet Kitchen   &  & &\fire\\
           &             & F\&C                  &\hl{\ch} &   &\fire\\
\inc      &B1         & Main Kitchen  & & &\fire\\
\inc      &B3         & Boiler Plant room & &&\fire\\
\bottomrule
\end{longtable}





