
\bgroup
\small
\label{chap:listofservices}

\begin{longtable}{llllp{3.9cm}}
%\begin{tabular}{llll}
\toprule
Ref	&Package	&Commiss.	&Perc. & Commissioning Status\\
     &         &Entity    &Compl.\\
\midrule
1.00	&\textbf{Mechanical}	&	&\\
1.01	&Chilled Water Systems	&CML	&25\% & Started. Valves arrived for Merweb risers. Hoping to free all Towers by end of January. \\
1.02	&Ductwork  &CML		&25\%  & Started. 30\% of all AHUs cleared for balancing.\\
1.03  &Kitchen Extract System &CML &25\% &Not started. Black steel ductwork still to complete. Level 8 louvres/plenum need to be completed. Expected start 13th February 2012.\\
1.04	&Car Park Ventilation 	&CML &25\% &Not started. Low priority for physical works. Expect to start commissioning 5th Floor 13th Feb. 2012.\\
1.05	&Gas Fired steam Boilers &Specialist&25\% &not started\\	
1.06	&Condenser Water System 	&CML&25 & Part of chilled water. Valves to be installed.\%     \\
1.07    &Cooling Tower &Specialist&25\% & Final parts for cooling Tower not cleared for delivery by Supplier. \\
\midrule
2.00	&\textbf{Electrical}		&& 70\% complete\\
2.01	&Standby Generators	&Specialist&100\% & Started on flushing for cooling towers. Commercial issues to be sorted out.\\	
2.02	&Medium Voltage System	&HS&25\% & Good progress all over. Panels missing and on order.\\	
2.03	&Low Voltage System		&HS&25\% & Started and commissioning progressively.\\
2.04	&Earthing \& Lightning Protection &HS&100\% &earthing mostly completed. Lightning protection, missing part on Shangrila\\		
2.05	&Lighting \& Emergency Lighting  &HS&100\% & Where possible started. Fit-out needs to be completed in a few areas.\\		
2.06	&Aircraft Warning System &HS&100\% & Ready. Supplier requested to visit and commission. Merweb support to be done.\\		
2.07	&UPS System	&Specialist&100\% & Not started. Incomplete and commercial issues.\\	
2.08 &Power Factor  &Specialist &100\% & Not started. Commercial issue.\\
\midrule
3.00	&Public Health		&&\\
3.01	&Potable Water	&HS&25\% & Not started. Ready for Kahraama possibly this week. Testing of Tanks, meeting with Metito, 16th Jan. \\	
3.02	&Above Ground Drainage &HS&25\% & Started.\\		
3.03	&Below Ground Drainage  &HS&25\% & Completed. Sump pumps commissioned.\\		
3.04	&Water Features	     &Specialist&100\% & not started\\	
3.05	&Gas Supply Installations	&Gasco&100\% & Not started. Can only start after Kitchen equipment. \\	
3.06 &Gray Water Treatment Plant&Metito&100\% & Not started. Will agree dates with Metito.\\
\midrule		
4.00	&Fire Defense &Nafco&100\% & Started. Naffco to supply missing electrical items. Low level zones cleared. Physical works to be completed.\\	
4.01	&FHC, FH and Sprinkler Installations	&Nafco&100\% & Started on Rotana. Nozzles still to be installed.\\	
4.02	&Smoke Exhaust		&HS/CML&100\% & started \\
4.03	&Staircase Pressurization          &HS/CML&100\% & Started in Rotana, measurements are low.\\		
4.04	&Fire Alarm		&Specialist&100\% & Not started.\\
4.05	&FM-200		&Nafco&100\% & Started on new schedule.\\
4.06	&Heliport Foam System	 &Nafco&100\% & Not physically ready\\	
\midrule
5.00	&Specialist Services		&&\\
5.01	&Building Management System	&Shajan/HS&25\% & Started. Shajan under performing.\\	
5.02	&Security Access Control \& CCTV	&Specialist/HS&100\% & Not started control rooms not ready.\\	
5.03	&CO Monitoring		&Specialist&100\% & Not started. Level 5 to be commissioned 13th February.\\
5.04	&Car Calling System		&Specialist&100\% & Unknown\\
5.05	&Lighting Control		&HS/Specilaist&25\% & not started\\
5.06	&Structured Cabling		&Specialist&25\% & Not started. Physical works incomplete.\\
5.07	&PA \& Background Music System &Specialist&25\% & Not started\\		
5.08	&IPTV \& Satellite System	&Specialist&100\% & not started. Order just closed. \\	
5.09	&Room Management System	&Specialist/HS&25\% & Not started. Constrained with Dragoni's works.\\
5.10 &Intercom                 &Specilaist/HS&25\% & Not started\\
5.11 &Audiovisual              &Specialist/HS&25\% & Not in scope\\
5.12 &Telephone                &Specialist/HS&25\% & Not started. Qtel room not ready. HVAC not delivered.\\
5.13 &Wi-fi                    &Specialist/HS&25\% & Not started\\
\midrule
6.00 &Other                    &			&\\
6.01 & BMU                     &Specialist/HEE &25\% & Not started\\
6.02 & Swimming Pool           &Specialist     &25\% & Not started\\
6.03 &Irrigation System        &Specialist     &25\% & Not started\\
\bottomrule
%\end{tabular}			
\end{longtable}
\egroup
