\section*{List of Services}


\captionof{table}{List of Services and approximate status of T\&C.}
\label{masterplan}
{\RaggedRight\small
\begin{longtable}{lllp{4.3cm}@{}}
%\begin{tabular}{llll}
\toprule
Ref	&Package	&T\&C	&Remarks\\
\midrule
1.00	&\textbf{Mechanical}	&	&\\
1.01	&Chilled Water Systems	&97\%	&Remaining, works closing of paper work or Askar related. See \refs{chilledwater}\\

1.02	&HVAC AHU  & 80\%		&  Remaining works, where final fixes are not completed. However, about 30\% of the units will have to have pulleys and or motors changed. See \refs{HVAC}.\\

1.03    &Kitchen Extract System &75\%& Following installation of ASKAR hoods. See \refs{kitchenextract}\\

1.03	&Car Park Ventilation 	&80\%&Smoke Tests remaining and some fans need remeasurements. See \refs{carparkventilation}\\

1.04	&Gas Fired Steam Boilers &50\%&Not possible to commission until we have gas on site. Gas will only be made available after Civil Defence inspection.	\\

1.05	&Condenser Water System 	&0\%&ASKAR have still not installed any of the related equipment. See \refs{chilledwaterconstraints}.    \\

1.06    &Cooling Tower &80\%&Chemical Treatment still to be commissioned. Live test still to be carried out, in tandem with generator sets. \ref{generators}.  \\
\midrule

2.00	&\textbf{Electrical}		&&\\
2.01	&Standby Generators	&30\%& Final live tests still remaining. See \sref{generators}. \\
	
2.02	&Medium Voltage System	&100\%&\\	

2.03	&Low Voltage System		&90\%&WIRs remaining.\\

2.04	&Earthing \& Lightning Protection &80\%&Lightning protection remaining. Expecetd to be commissioned by 30 Mar 2013.\\		

2.05	&Lighting \& Emergency Lighting  &70\%& Exit lights, progressively carried out. Emergency lighting to be commissioned after Generator live test.\\		

2.06	&Aircraft Warning System &0\%& Expected to be commissioned by 20 Apr 2013.\\	
	
2.07	&UPS System	&70\%&  Merweb remaining due to EI, expected to be commissioned by 30 Mar 2013.\\	
\midrule
3.00	&\textbf{Public Health}		&&\\
3.01	&Potable Water	&65\%& Delays due to Final fixture installation. Expected to start commissioning late April.\\	

3.02	&Above Ground Drainage &80\%&20\% to be carried out once all sanitary fittings are completed.\\		
3.03	&Below Ground Drainage  &100\%&\\		
3.04	&Water Features	     &0\%& HLG scope\\	
3.05	&Gas Supply Installations	&0\%& Cannot get gas until Civil Defence Inspection. Earliest start date 10 May 2013.\\	
3.06  & Gray Water Treatment &0\% &EI works for changing sectional tanks to concrete. Earliest start 20 April 2013.  \\
\midrule		
4.00	&\textbf{Fire Defense} &&\\	
4.01	&FHC, FH and Sprinkler Installations.	&80\%&Closing paper work and work progresses with Final fixes.\\	
4.02	&Smoke Exhaust		&70\%&Fans underperforming, leakage on ducts. \\
4.03	&Staircase Pressurization          &85\%&All completed but retesting is necessary.\\		
4.04	&Fire Alarm		&50\%& Works are progressively carried out (see \S\ref{sec:firealarm}). Also awaiting for materials.\\

4.05	&FM-200		&70\%&Integrity tests being carried out. Going well. \\

4.06	&Heliport Foam System	 &0\%&Issue with missing materials (Naffco).\\	
\midrule
5.00	&\textbf{Specialist Services}		&&\\
5.01	&Building Management System	&75\%& Going well.\\	
5.02	&Security Access Control \& CCTV	&0\%&Client scope, now.\\	
5.03	&CO Monitoring		& 30\%&Manufacturer to start commissioning 13 Mar 2013 \\
5.04	&Car Calling System		&0\%&Manufacturer ready to commission.\\

5.05	&Lighting Control		&0\%&Subject to finishes\\

5.06	&Structured Cabling		&40\%&Progressively tested. Affected by integration EI. Expected completion 20-30 Apr 2013\\

5.07	&PA \& Background Music System &0\%& Not in HLS scope. Interfacing with  FA ongoing.\\		
5.08	&IPTV \& Satellite System	&0\%&Physical works dirsupted by EI as for 5.06.\\	
5.09	&Room Management System	&30\%&Delayed due to Dragoni works.\\

\bottomrule
%\end{tabular}			
\end{longtable}
}

