%%
% MERWEB TOWER PROGRESS REPORT
\chapter{Merweb Tower}

\newthought{The Merweb physical} installations are estimated as 95\% completed. Progress on the Tower has been suffering due to JEM having reduced personnel a number of times due to commercial issues. The current work force on site is 26 personnel, which is totally inadequate for the works.
Of concern are works still in shafts and works affecting follow-up trades. Our recommendation is to add HS personnel to assist the works.

\index{Towers!Merweb Progress}

\section{Additional Works}

List of recent EIs.


%\begin{table}[htbp]
%\small\RaggedRight
%\begin{tabular}{@{}llp{3cm}p{3cm}}
%\toprule
%Date &RFI No. &Description &Remarks\\
%\midrule
%5/1/2012 &RFI 901-E-1424  &Level 24 add four lights &EI-724 to follow.\\
%\bottomrule
%\end{tabular}
%\caption{List of recently received RFI replies for Rotana Tower. The number of RFIs have now been reduced.}
%\end{table}


\section{By System}
This part of outstanding activities is sorted by service. Oustanding activities and constraints are outlined under remarks. 
\bigskip

\begin{fullwidth} 
\captionof{table}{Outstanding Works by System. This is a summary of main points. The person responsible to close the issue and report weekly is shown in colour.}
\label{SLsystems}
\RaggedRight\small
\begin{longtable}{@{}lp{3.5cm}@{}lp{5cm}p{3.5cm}}

%\begin{tabular}{llll}
\toprule
Ref	&Package	& &Outstanding Works& Responsibility\\
\midrule
1.00	&\textbf{Mechanical}	&	&&\\
1.01	&Chilled Water Systems	&	& &\Nidhal\\
1.02	&Ductwork (Air side)  &		& &\George\\
1.03    &Kitchen Extract System && N/A&\\
1.03	&Car Park Ventilation 	&&N/A&\\
1.04	&Gas Fired steam Boilers &&N/A&		\\
1.05	&Condenser Water System 	&&N/A&    \\
1.06    &Cooling Tower &&N/A&  \\
\midrule
2.00	&\textbf{Electrical}		&&\\
2.01	&Standby Generators	&&N/A&\\	
2.02	&Main Power	&& \\	
2.03	&Small Power	&&Final fix 7-47 lights not fully installed. & \\
2.04	&Earthing \& Lightning Protection &&&\Nidhal \\		
2.05	&Lighting & &FCU bulkhead lights. EI 200, 201, 202 and EI 160.&\Nidhal \\
2.06	&Aircraft Warning System &&Obstruction lights. &\Nidhal to confirm completion and summarize all WIRs.\\		
2.07	&UPS System	&&&\Nidhal\\	
2.08   &Signage      &&.&\Nidhal\\
2.09   &Facade lighting &&Apparently not being able to install due to aluminium.  &\\
\midrule
3.00	&\textbf{Public Health}		&&&\\
3.01	&Potable Water	&&Installation of BFPV, provision of eye wash (EI 193). Manifold connection, ring main connections. PPR risers level 23-17. L25-41 kitchen sink connections. & \Sripathy \\	
       &Sanitary Final Fix &&Janitor's sinks. Level 43-7. Bathroom accessories Levels 35-7. Counter sink bathroom with accessories 43-7.& \Sripathy to conduct full survey and inspection. Counter sink not available.\\
3.02	&Above Ground Drainage &&Vent cowls. AHU rooms drains. Flow testing. Riser connections shaft 2 \& 3. Male female bathrooms level 24. AFD Kitchen Level 24. Level 43-47 incomplete installation.& \Sripathy\\		
3.03	&Below Ground Drainage  && N/A&\\		
3.04	&Water Features	     && N/A&\\	
3.05	&Gas Supply Installations	&&N/A &\\	
\midrule		
4.00	&\textbf{Fire Defense} &&&\\	
4.01	&FHC, FH and Sprinkler Installations	&&FHC accessories. Rectifications to sprinkler works. FOR Shaft 6. Alarm check valve.  &\Jeffrey \\	
4.02	&Smoke Exhaust		&&Incomplete works on top.&\\
4.03	&Staircase Pressurization          &&Final fix installation. Stops commissioning.&\George\\		
4.04	&Fire Alarm		&&EI 151, EI 177, EI 192, EI 196 incomplete. &\Nidhal to produce full survey of current installation.\\
4.05	&FM-200		&&N/A&\\
4.06	&&\\
4.07   & Emergency lighting &&&\Nidhal\\	
\midrule
5.00	&\textbf{Specialist Services}&&\\
5.01	&Building Management System	&&DDC installation and testing incomplete. &\John to produce detail report floor by floor. Installation and dressing and testing for DDCP. JEM estimate these works at 180 days.  \\	
5.02	&Security Access Control \& CCTV	&&&\\	
5.03	&CO Monitoring		&&N/A&\\
5.04	&Car Calling System		&&N/A&\\
5.05	&Lighting Control		&&N/A&\\
5.06	&Structured Cabling		&&& \Nidhal\\
5.07	&PA \& Background Music System &&N/A&\\		
5.08	&IPTV \& Satellite System	&&Status incomplete&\Nidhal to summarize requirements. \\	
5.09	&Room Management System	&&N/A&\Rahul\\
5.10 &Media hub && .&\Nidhal \\
5.11 &Telephone \& Data &&Completion of snags.&\\

\bottomrule
%\end{tabular}	
\end{longtable}
\end{fullwidth}

\small
\begin{table}[htbp]
\caption{Merweb Ceiling and Wall Closure Plan}
\begin{tabular}{llllll}
\toprule 
\multicolumn{6}{c}{\bf Merweb Ceiling and Wall Closure}\\
\midrule
~        & Corridor & Pass. lift  & Serv. lift  & Rooms   & Dry walls \\
Level   &            & lobby             &lobby    &    &              \\ 
\midrule
Lvl 43  &             &                &                &             &              \\
Lvl 42  &	  &		&	&	&	\\
Lvl 41  &             &              &         &     &        \\
Lvl 40  & \done     &\done&\done&\done&\done\\
Lvl 39  & \done     &\done&\done&\done&\done\\
Lvl 38  & \done     &\done&\done&\done&\done\\
Lvl 37  & \done     &\done&\done&\done&\done\\
Lvl 36  & \done     &\done&\done&\done&\done\\
Lvl 35  & \done     &\done&\done&\done&\done\\
Lvl 34  & \done     &\done&\done&\done&\done\\
Lvl 33  & \done     &\done&\done&\done&\done\\
Lvl 32  & \done     &\done&\done&\done&\done\\
Lvl 31  & \done     &\done&\done&\done&\done\\
Lvl 30  & \done     &\done&\done&\done&\done\\
Lvl 29  & \done     &\done&\done&\done&\done\\
Lvl 28  & \done     & \done          &\done         &\done        &\done\\
Lvl 27  & \done    & \done   &\done         &\done         &\done \\
Lvl 26  & \done    & \done  & \done        &\done         &\done \\
Lvl 25  & 4 Aug    & \done  & \done        &done         &\done \\
Lvl 24  & 7 Aug    & 7 Aug  & 7 Aug        &7 Aug         &\done \\
Lvl 23  & 9 Aug    & 9 Aug  & 9 Aug        &9 Aug         & 24 Jul\\
Lvl 22  & 11 Aug   &11 Aug & 11 Aug        &11 Aug         &26 Jul\\
Lvl 21  & 14 Aug   &14 Aug  & 14 Aug        &14 Aug         &28 Jul\\
Lvl 20  & 16 Aug   &16 Aug          &16 Aug         &16 Aug         &30 Jul\\
Lvl 19  & 18 Aug   &18 Aug           &18 Aug         &18 Aug         &1 Aug\\
Lvl 18  & 21 Aug   &21 Aug & 21 Aug                  &21 Aug         &3 Aug\\
Lvl 17  & 23 Aug   &23 Aug  &23 Aug         &23 Aug         &5 Aug\\
Lvl 16  & 25 Aug   &25 Aug  &25 Aug         &25 Aug         &7 Aug\\
Lvl 15  & 27 Aug   &27 Aug  &27 Aug         &27 Aug         &9 Aug\\
Lvl 14  & 30 Aug   &30 Aug  &30 Aug         &30 Aug         &11 Aug\\
Lvl 13  & 1 Sep     &1 Sep    &1 Sep         &1 Sep         &13 Aug\\
Lvl 12  & 4 Sep     &4 Sep    & 4 Sep        &4 Sep         &15 Aug\\
Lvl 11  & 6 Sep     &6 Sep    & 6 Sep        &6 Sep         &17 Aug\\
Lvl 10  & 8 Sep     &8 Sep    & 8 Sep        &8 Sep         &19 Aug\\
Lvl 09  & 10 Sep   &10 Sep   & 11 Sep        &11 Sep         &21 Aug\\
Lvl 08  & 12 Sep   &12 Sep   & 13 Sep        &13 Sep         &23 Aug\\
Lvl 07  & 15 Sep   &15 Sep   & 15 Sep        &15 Sep         &25 Aug\\
\bottomrule
\end{tabular}
\normalsize
\end{table}

\out{Rotana Tower Completion : }{15 Sep 2010}

