%%
% ROTANA TOWER PROGRESS REPORT
\chapter{Rotana Tower}

\newthought{The physical completion} of the works is currently estimated at 97\%. Works remaining are mostly final fix activities, which cannot be completed until such time as the Owner's Direct Contractor completes his portion of the works.
Closure of the works is hampered due to  Crompton's poor performance. Commissioning of Electrical systems, fan-coil-units and BMS has started and is well advanced. ELV works are hampered by changes. Target completion---as far as we can go---is estimated at 13th February 2012. Currently Crompton average 36 personnel on site. The number of personnel are inadequate to assist with commissioning attendance and close snagging, although they will manage to complete the bulk of the items in the outstanding list.

\section{Additional Works}

List of recent EIs.


\begin{table}[htbp]
\small\RaggedRight
\begin{tabular}{@{}llp{3cm}p{3cm}}
\toprule
Date &RFI No. &Description &Remarks\\
\midrule
5/1/2012 &RFI 901-E-1424  &Level 24 add four lights &EI-724 to follow.\\
\bottomrule
\end{tabular}
\caption{List of recently received RFI replies for Rotana Tower. The number of RFIs have now been reduced.}
\end{table}


\section{By System}
This part of outstanding activities is sorted by service. Oustanding activities and constraints are outlined under remarks. 
\bigskip

\begin{fullwidth} 
\captionof{table}{Outstanding Works by System. This is a summary of main points. The person responsible to close the issue and report weekly is shown in colour.}
\label{SLsystems}
\RaggedRight
\begin{longtable}{@{}lp{3.5cm}@{}lp{5cm}p{3.5cm}}
%\begin{tabular}{llll}
\toprule
Ref	&Package	& &Outstanding Works& Responsibility\\
\midrule
1.00	&\textbf{Mechanical}	&	&&\\
1.01	&Chilled Water Systems	&	&Quick fill, AAV, GV, identification labels. Installation of DRV L-43, inaccessible. System is operational. Confirmation of completion of snag items issued by CML. &\Nidhal\\
1.02	&Ductwork (Air side)  &		& L47 and L-44 completion and inspection. To be snagged by HS. Level 24 ducting.&\George\\
1.03    &Kitchen Extract System && N/A&\\
1.03	&Car Park Ventilation 	&&N/A&\\
1.04	&Gas Fired steam Boilers &&N/A&		\\
1.05	&Condenser Water System 	&&N/A&    \\
1.06    &Cooling Tower &&N/A&  \\
\midrule
2.00	&\textbf{Electrical}		&&\\
2.01	&Standby Generators	&&N/A&\\	
2.02	&Medium Voltage System	&& Bus duct commissioning completed. &\Nidhal to confirm and summarize all WIRs in a report.\\	
2.03	&Low Voltage System		&& DB dressing at level 42 and 43 Electrical room.&\Nidhal to confirm through WIRs and full schedule.\\
2.04	&Earthing \& Lightning Protection &&Installation of lightning arrestor.&\Nidhal \\		
2.05	&Lighting & &FCU bulkhead lights.&\Nidhal \\
2.06	&Aircraft Warning System && Photocell to be installed. &\Nidhal to confirm completion and summarize all WIRs.\\		
2.07	&UPS System	&&&\Nidhal\\	
2.08   &Signage      &&.&\Nidhal\\
\midrule
3.00	&\textbf{Public Health}		&&&\\
3.01	&Potable Water	&& & \Sripathy \\	
3.02	&Above Ground Drainage && Kitchen waste, CI from levels 8-44. Vent pipes 48-49, see also level 40 and level 48 (awaiting tiling layout).& \Sripathy\\		
3.03	&Below Ground Drainage  && N/A&\\		
3.04	&Water Features	     && N/A&\\	
3.05	&Gas Supply Installations	&& &\\	
\midrule		
4.00	&\textbf{Fire Defense} &&&\\	
4.01	&FHC, FH and Sprinkler Installations	&& Complete snagging of system. Accessibility to valves.&\Jeffrey \\	
4.02	&Smoke Exhaust		&&&\\
4.03	&Staircase Pressurization          &&&\George\\		
4.04	&Fire Alarm		&&Incomplete cable pulling at ELV riser &\Nidhal\\
4.05	&FM-200		&&N/A&\\
4.06	&&\\
4.07   & Emergency lighting &&Exit lights. L44 Glass wall light fitting Type-M&\Nidhal\\	
\midrule
5.00	&\textbf{Specialist Services}&&\\
5.01	&Building Management System	&& Commissioning report pending. See chart for BMS per floor. Thermostat installation. Relocation of FCU controller from L30-L34.&\John \\	
5.02	&Security Access Control \& CCTV	&&Installation of battery back-up for access control syste. Material issue. Card readers and push buttons at corridor areas incomplete due to wall paper not completed.&\\	
5.03	&CO Monitoring		&&N/A&\\
5.04	&Car Calling System		&&N/A&\\
5.05	&Lighting Control		&&N/A&\\
5.06	&Structured Cabling		&&& \Nidhal\\
5.07	&PA \& Background Music System &&N/A&\\		
5.08	&IPTV \& Satellite System	&&&\\	
5.09	&Room Management System	&&N/A&\Rahul\\
5.10 &Media hub && .&\Nidhal \\
5.11 &Telephone \& Data &&Completion of snags.&\\

\bottomrule
%\end{tabular}	
\end{longtable}
\end{fullwidth}




\begin{table}[htbp]
\small
\caption{Rotana Ceiling and Wall Closure Plan}
\begin{tabular}{llllll}
\toprule 
\multicolumn{6}{c}{\bf Rotana Ceiling and Wall Closure}\\
\midrule
~        & Corridor & Pass. lift  & Serv. lift  & Rooms   & Dry walls \\
Level   &            & lobby             &lobby    &    &              \\ 
\midrule
Lvl 43  &             &                &                &             &              \\
Lvl 41  &             &              &         &     &        \\
Lvl 40  & \done     &\done&\done&\done&\done\\
Lvl 39  & \done     &\done&\done&\done&\done\\
Lvl 38  & \done     &\done&\done&\done&\done\\
Lvl 37  & \done     &\done&\done&\done&\done\\
Lvl 36  & \done     &\done&\done&\done&\done\\
Lvl 35  & \done     &\done&\done&\done&\done\\
Lvl 34  & \done     &\done&\done&\done&\done\\
Lvl 33  & \done     &\done&\done&\done&\done\\
Lvl 32  & \done     &\done&\done&\done&\done\\
Lvl 31  & \done     &\done&\done&\done&\done\\
Lvl 30  & \done     &\done&\done&\done&\done\\
Lvl 29  & \done     &\done&\done&\done  &\done\\ont
Lvl 28  & \done     & 27 Jul          &27 Jul         &27 Jul &\done\\
Lvl 27  & 29 Jul    & 29 Jul   &29 Jul         &29 Jul         &\done \\
Lvl 26  & 2 Aug    & 2 Aug  & 2 Aug        &2 Aug         &\done \\
Lvl 25  & 4 Aug    & 4 Aug  & 4 Aug        &4 Aug         &\done \\
Lvl 24  & 7 Aug    & 7 Aug  & 7 Aug        &7 Aug         &\done \\
Lvl 23  & 9 Aug    & 9 Aug  & 9 Aug        &9 Aug         & \done \\
Lvl 22  & 11 Aug   &11 Aug & 11 Aug        &11 Aug         &\done \\
Lvl 21  & 14 Aug   &14 Aug  & 14 Aug        &14 Aug         &\done \\
Lvl 20  & 16 Aug   &16 Aug          &16 Aug         &16 Aug         &30 Jul\\
Lvl 19  & 18 Aug   &18 Aug           &18 Aug         &18 Aug         &1 Aug\\
Lvl 18  & 21 Aug   &21 Aug & 21 Aug                  &21 Aug         &3 Aug\\
Lvl 17  & 23 Aug   &23 Aug  &23 Aug         &23 Aug         &5 Aug\\
Lvl 16  & 25 Aug   &25 Aug  &25 Aug         &25 Aug         &7 Aug\\
Lvl 15  & 27 Aug   &27 Aug  &27 Aug         &27 Aug         &9 Aug\\
Lvl 14  & 30 Aug   &30 Aug  &30 Aug         &30 Aug         &11 Aug\\
Lvl 13  & 1 Sep     &1 Sep    &1 Sep         &1 Sep         &13 Aug\\
Lvl 12  & 4 Sep     &4 Sep    & 4 Sep        &4 Sep         &15 Aug\\
Lvl 11  & 6 Sep     &6 Sep    & 6 Sep        &6 Sep         &17 Aug\\
Lvl 10  & 8 Sep     &8 Sep    & 8 Sep        &8 Sep         &19 Aug\\
Lvl 09  & 10 Sep   &10 Sep   & 11 Sep        &11 Sep         &21 Aug\\
Lvl 08  & 12 Sep   &12 Sep   & 13 Sep        &13 Sep         &23 Aug\\
Lvl 07  & 15 Sep   &15 Sep   & 15 Sep        &15 Sep         &25 Aug\\
\bottomrule
\end{tabular}
\normalsize
\end{table}




















