%%
% ROTANA TOWER PROGRESS REPORT
\chapter{Rotana Tower}

\newthought{The physical completion} of the works is currently estimated at 98.5\%. Works remaining are mostly final fix activities\sidenote{These follow the progress of Dragoni.} and snags arising out of commissioning reports. There works will be completed when the Owner's Direct Contractor completes their portion of the works.\sidenote{This mostly affects final fix of wiring accessories, sprinklers and grilles.} 

Closure of the works was earlier hampered due to  Crompton's poor performance. Action has been taken to supplement their labour with HLS technicians, where required.

Commissioning of Electrical systems, fan-coil-units and BMS has started and is mostly completed.  CCTV works are on hold until such time as the Owner's Direct Contractor has mobilized. Target completion final completion and ready for hand-over\sidenote{Except IPTV, CCTV, telephones which were subjected to new EIs.} and Civil Defence Inspection readiness for this Tower is estimated at 30th March 2013.\sidenote{Subject to Dragoni completing their works and allowing adequate time for follow-up activities.} 


\section{Current Status of Works}

The current status of works is summarized in Table~\ref{tbl:RObalance}

\bigskip

%\begin{fullwidth} 
\small
\captionof{table}{Outstanding Works by System. This is a summary of main points. The person responsible to close the issue and report weekly is shown in colour.}
\label{SLsystems}
\RaggedRight
\begin{longtable}{@{}cp{3.5cm}@{}cp{.7cm}p{3cm}}
%\begin{tabular}{llll}
\toprule
Ref	&Package	&Phys. Works & T\&C & Remarks\\
\midrule
1.00	&\textbf{Mechanical}	&	&&\\
1.01	&Chilled Water Systems	
      &\checkmark	
      &\checkmark 
      & GG to close. \\
1.02	&Ductwork (Air side)  
      &\checkmark		
      &\checkmark 
      & Final fix in certain areas is incomplete 
        due to Dragoni works. T\&C measurements taken. \\
\midrule
2.00	&\textbf{Electrical}	& &\\
2.01	&Medium Voltage System	
      &\checkmark & \checkmark 
      & Summary WIRs.\\	

2.03  &Low Voltage System		
      &\checkmark & \checkmark.
      & Final accessories in some areas 
        incomplete due to Dragoni works.\\

2.04	&Earthing \& Lightning Protection   
      &\checkmark
      &X
      & Nidhal (Summary WIR). Commissioning to start.\\
		
2.05	&Lighting 
      &\checkmark
      &\checkmark& Nidhal \\

2.06	&Aircraft Warning System 
      &\checkmark
      &X &Nidhal arrange commissioning.\\	
	
2.08   &Signage      &&.& Nidhal\\
\midrule
3.00	&\textbf{Public Health}		&&&\\
3.01	&Potable Water	
      &\checkmark
      &X 
      & Sripathy \\	
3.02	& Sanitary Fixtures and Fittings 
      & X
      & X
      & Sripathy. Missing materials.\\		
\midrule		

4.00	&\textbf{Fire Defense} 
      &
      &
      &\\	

4.01	&FHC
      &\checkmark
      &\checkmark
      &Hose-rack nozzles to be replaced.\\ \\
	
4.02	&Smoke Exhaust		
      &\checkmark
      &\checkmark
      &\\

4.03	&Staircase Pressurization          
      &\checkmark
      &\checkmark
      & Retesting 5 Mar 2013.\\	
	
4.04	&Fire Alarm	
      &\checkmark
      &IP 
      &Nidhal\\

4.05   & Exit lighting 
       & \checkmark
       &  
       & Nidhal\\	

\midrule
5.00	&\textbf{Specialist Services}&&\\
5.01	&Building Management System	
       &\checkmark
       &\checkmark &Jabir (summary) \\	
5.02	&Security Access Control \& CCTV	
       & X
       & X.
       & EI works\\	
5.05	&Lighting Control		&&N/A&\\
5.06	&Structured Cabling		
      &X
      &X
      & Nidhal\\
5.07	&PA \& Background Music System &&N/A&\\		
5.08	&IPTV \& Satellite System	
      & \checkmark
      & X
      & EI integration, balance works\\	

5.09  &Telephone \& Data 
      &X
      &X
      &report available\\

\bottomrule
%\end{tabular}	
\caption{Summary of pending works}
\label{tbl:RObalance}
\end{longtable}
%\end{fullwidth}






\section{Final Snag List}

\begin{table}[htbp]
\begin{tabular}{lllp{4.5cm}}
\toprule
Item &Detail &Floor  & Remarks\\
\midrule
1 &Final Wiring Accessories &L8-25,42,43 & Subject to Dragoni \\
2 &Vestibule Lighting       & ditto      &      ditto\\
3 &UNC installation         & all        & will be installed during commissioning\\
4  &Floor boxes              &all         &material issue\\
5  &BMS ferrules             &all         & ditto\\
\bottomrule
\end{tabular}
\caption{Final Snag List Electrical, Rotana}
\end{table}

\begin{table}[htbp]
\begin{tabular}{lllp{4.5cm}}
\toprule
Item &Detail &Floor  & Remarks\\
\midrule
1 &FF sanitary &various & Material issue as per email to HLG, 9.01.2013. \\
\bottomrule
\end{tabular}
\caption{Final Snag List mechanical, Rotana}

\end{table}


\section{Paperwork}

\subsection{NCR\&FORs}

These have now been closed. 

\begin{comment}
\begin{table}[htbp]
\small
\begin{tabular}{lp{3.5cm}llp{2.5cm}}
\toprule
Item &NCR & Levels & Status &Remarks\\ 
\midrule
1    &Fire alarm cables and belden cables pulled in same cable tray and CCTV without containment inside ELV room. 
& all & &superceded by events, due to new EI.\\
\bottomrule
\end{tabular}
\caption{List of outstanding electrical NCRs, Rotana Tower}
\end{table}
\end{comment}

We expecting all documentation for closure of outstanding NCRs and FORs to be completed by 31.01.2013.
















