%%
% MERWEB TOWER PROGRESS REPORT
\chapter{Merweb Tower}

\newthought{The Merweb physical} installations are estimated as 97\% completed. Progress on the Tower has been suffering due to JEM having reduced personnel a number of times due to commercial issues. The current work force on site is 26 personnel, which is inadequate for the works. Of concern are works still in shafts and works affecting follow-up trades. We have been promised additional personnel at our last meeting (26 Feb 2013).

\index{Towers!Merweb Progress}

%\section{Additional Works}
%
%List of recent EIs.


%\begin{table}[htbp]
%\small\RaggedRight
%\begin{tabular}{@{}llp{3cm}p{3cm}}
%\toprule
%Date &RFI No. &Description &Remarks\\
%\midrule
%5/1/2012 &RFI 901-E-1424  &Level 24 add four lights &EI-724 to follow.\\
%\bottomrule
%\end{tabular}
%\caption{List of recently received RFI replies for Rotana Tower. The number of RFIs have now been reduced.}
%\end{table}


\section{By System}
This part of outstanding activities is sorted by service. Oustanding activities and constraints are outlined under remarks. 
\bigskip




\begin{fullwidth} 
\captionof{table}{Outstanding Works by System. This is a summary of main points. }
\label{SLsystems}
\RaggedRight\small
\setcounter{step}{0}
\begin{longtable}{@{}lp{2.8cm} c l lp{3.2cm} }
\toprule
Ref	&Package	 &Inst. & T\&C  &\WIR &Remarks \\
\tablesection

\Inc	&\textbf{Mechanical}	&	&&&\\
\Inc	&Chilled Water Systems	&\checkmark	&\checkmark&&  \\
\Inc	&Ductwork (Air side)  &\checkmark		& && \\
\Inc  &Kitchen Extract System & \checkmark & &&\\

\tablesection
\Inc	&\textbf{Electrical}		&&&&\\
\Inc	&DBs energized	&\checkmark &&& \\	
\Inc	&Small Power	&50\%&&&Final fix pending \\
\Inc	&Earthing \& Lightning Protection &\checkmark&&&Lightning protection pending.  \\		
\Inc	&Lightning Protection&\checkmark&&& \\
\Inc	&Aircraft Warning System \&Obstruction lights. &\checkmark&&&Creo notified 26 Feb 2013, issue with pre-payment for commissioning.  \\		
\Inc   &Signage      &&&&Power provision only \\
\Inc   &Facade lighting &\checkmark & \checkmark &&\\

\tablesection
\Inc	&\textbf{Public Health}		&&&&\\
\Inc	&Potable Water	&\checkmark&&& \\	
       &Sanitary Final Fix &x&&&\\
\Inc	&Gas Supply Installations	&\checkmark & &&\\
\Inc &Gas Supply final hook-up & x         &x& \\	

\tablesection		
\Inc	&\textbf{Fire Defense} &&&&\\	
\Inc	&FHC, FH and Sprinkler Installations	&\checkmark&\checkmark&&25 Mar 2013 \\	

\Inc	&Smoke Exhaust &\checkmark & & &Rectification works.\\

\Inc	&Staircase Pressurization  &\checkmark& &&See \refs{pressurization} page \pageref{pressurization} for details. \\	
	
\Inc	&Fire Alarm		&\checkmark&&&See \refs{firealarm} \\


\Inc   & Emergency lighting &\checkmark&&& 20.03.2013 (material?) \\	

\tablesection
\Inc	&\textbf{Specialist Services}&&&\\

\Inc	&Building Management System	&\checkmark&75\%&& \\	

\Inc	&Security Access Control \& CCTV	&& &&Owner's subcontractor.\\	

\Inc	&Lighting Control		&&&&Nidhal to advice.\\

\Inc	&Telephone and Data	&60\%&&&Infosphere delays, due to convergent networks.\\
\Inc &Media hub &90\%& && \\


\Inc	& Background Music System &&&&\\		

\Inc	&IPTV \& Satellite System	&&&&Rahul to follow. \\	


\bottomrule
%\end{tabular}	
\end{longtable}
\end{fullwidth}



