\chapter{SHANGRILA TOWER}

\newthought{The physical installation} of the Shangrila Tower works are currently estimated at 97\% completion. Remaining items are described in the sections below.  Most of the remaining items  are constrained on non-personnel related issues. Commissioning has commenced for some of the mechanical systems (water, fan-coil units). Issues that affect Testing and Commissioning are described in Table~\ref{SLsystems}. Currently QMMC averages 63 personnel on site. 

\section{Issues with HOK}

\begin{enumerate}
\item EI No. 358 additional funnel drain for Ice Maker, affecting floors L41-L22 HK and Chute area.
\item EI No. 228 additional funnel drain for Ice Maker, near shaft 2. Instead of funnel drain normal drain was installed. Floor 9-21.
\end{enumerate}


\begin{table}[htbp]
\small\RaggedRight
\begin{tabular}{@{}llp{3cm}p{3cm}}
\toprule
Date &EI No. &Description &Remarks\\
\midrule
5/1/2012 &EI 709  &Additional smoke extract system &EI-709 affcecting LV 42 \&43. Correspondence HOK/225/L3239, HEE 14393.\\
\bottomrule
\end{tabular}
\caption{List of recently received RFI replies for Rotana Tower. The number of RFIs have now been reduced.}
\end{table}
\section{ID}
Level 48 Powder room SL4803 to be completed. Awaiting civil work tiling prior to installation.

%%
% SHANGRILA TOWER PROGRESS REPORT

\begin{table}[htbp]
\small
\caption{Shangri-la Ceiling and Wall Closure Plan}
\begin{tabular}{lllllp{3.5cm}}
\toprule 
\multicolumn{6}{c}{\bf Shangri-la Ceiling and Wall Closure}\\
\midrule
~        & Corridor & Pass. lift  & Serv. lift  & Rooms   & Dry walls \\
Level   &            & lobby             &lobby    &    &              \\ 
\midrule
Lvl 44  &             &                &                &             &              \\
Lvl 43  &             &                &                &             &              \\
Lvl 41  &             &              &         &     &\done        \\
Lvl 40  & \done     &\done&\done&\done&\done\\
Lvl 39  & \done     &\done&\done&\done&\done\\
Lvl 38  & \done     &\done&\done&\done&\done\\
Lvl 37  & \done     &\done&\done&\done&\done\\
Lvl 36  & \done     &\done&\done&\done&\done\\
Lvl 35  & \done     &\done&\done&\done&\done\\
Lvl 34  & \done     &\done&\done&\done&\done\\
Lvl 33  & \done     &\done&\done&\done&\done\\
Lvl 32  & \done     &\done&\done&\done&\done\\
Lvl 31  & \done     &\done&\done&\done&\done\\
Lvl 30  & \done     &\done&\done&\done&\done\\
Lvl 29  & \done     &\done&\done&\done  &\done\\
Lvl 28  & \done     & 27 Jul          &27 Jul         &\done &\done\\
Lvl 27  & \done    & 29 Jul   &29 Jul         &29 Jul         &\done \\
Lvl 26  & \done   & 2 Aug  & 2 Aug        &2 Aug         &\done \\
Lvl 25  & 22 Jul    & 4 Aug  & 4 Aug        &4 Aug         &\done \\
Lvl 24  & 27 Jul    & 7 Aug  & 7 Aug        &7 Aug         &\done \\
Lvl 23  & 27 Jul    & 9 Aug  & 9 Aug        &9 Aug         & \done \\
Lvl 22  & 03 Aug   &04 Aug & 11 Aug        &11 Aug         &\done \\
Lvl 21  & \done   &14 Aug  & 14 Aug        &14 Aug         &\done \\
Lvl 20  & 04 Aug   &09 Aug          &16 Aug         &16 Aug         &\done \\
Lvl 19  & 09 Aug   &28 Jul           &18 Aug         &18 Aug         &1 Aug\\
Lvl 18  & 28 Jul   &29 Jul & 21 Aug                  &21 Aug         &3 Aug\\
Lvl 17  & 29 Jul   &23 Aug  &23 Aug         &23 Aug         &\done \\
Lvl 16  & 01 Aug   &01 Aug  &25 Aug         &25 Aug         &\done \\
Lvl 15  & 01 Aug   &01 Aug  &27 Aug         &27 Aug         &9 Aug\\
Lvl 14  & 30 Aug   &03 Aug  &30 Aug         &30 Aug         &11 Aug\\
Lvl 13  & 03 Aug     &03 Aug    &1 Sep         &1 Sep         &13 Aug\\
Lvl 12  & 03 Aug     &06 Aug    & 4 Sep        &4 Sep         &\done \\
Lvl 11  & 06 Aug     &06 Aug    & 6 Sep        &6 Sep         &\done \\
Lvl 10  & 06 Aug     &06 Aug    & 8 Sep        &8 Sep         &19 Aug\\
Lvl 09  & 09 Aug   &09 Aug   & 11 Sep        &11 Sep         &21 Aug\\
Lvl 08  & 12 Aug   &12 Aug   & 13 Sep        &13 Sep         &23 Aug\\
\bottomrule
\end{tabular}
\normalsize
\end{table}


\section{By System}
This part of outstanding activities is sorted by service. Oustanding activities and constraints are outlined under remarks. 
\bigskip

\begin{fullwidth} 
\captionof{table}{Outstanding Works by System. This is a summary of main points. The person responsible to close the issue and report weekly is shown in colour.}
\label{SLsystems}
\RaggedRight
\begin{longtable}{@{}lp{3.5cm}@{}lp{5cm}p{1.5cm}}
%\begin{tabular}{llll}
\toprule
Ref	&Package	& &Outstanding Works& Responsibility\\
\midrule
1.00	&\textbf{Mechanical}	&	&&\\
1.01	&Chilled Water Systems	&	&Quick fill, AAV, GV, identification labels. None affecting commissioning. System is operational. &\\
1.02	&Ductwork (Air side)  &		& L48, minor works. L8-L45, fire dampers missed. Work on-going not affecting commissioning.3 No. VFD panels level 44-47 pending affecting system commissioning. AHU heater terminations, incomplete.&\\
1.03    &Kitchen Extract System && ECUs installed, black steel ducting completed. Insulation and inspections to be completed.&\\


\midrule
2.00	&\textbf{Electrical}		&&\\
2.02	&Medium Voltage System	&& Bus duct commissioning completed. Level 42-43, 25 mm armoured cable glands.&\\	
2.03	&Low Voltage System		&& 45A DP EI-632E at levels 18, 19 and 41. Materials unavailability.&\\
2.04	&Earthing \& Lightning Protection &&& \\		
2.05	&Lighting && Core shafts bulk-heads EI-179. Dimmer DBs L42-43.& \\
2.06	&Aircraft Warning System && Completed. To be commissioned.& \\		
2.07	&UPS System	&&N/A Level 42 5kVA UPS not installed. Material not available.& \\	
2.08   &Signage      &&Signage lights for 63A (water proof) isolator not done (Level 45). Material issue. Sanitary final fix to be confirmed.& \\
\midrule
3.00	&\textbf{Public Health}		&&&\\
3.01	&Potable Water	&& L47, L48 Water hammer arrestor. Service shafts remedial works, affecting L8-34. Identification, completeness report.&  \\	
3.02	&Above Ground Drainage && Kitchen waste, CI from levels 8-44. Vent pipes 48-49, see also level 40 and level 48 (awaiting tiling layout).& \\		
3.03	&Below Ground Drainage  && N/A&\\		
3.04	&Water Features	     && N/A&\\	
3.05	&Gas Supply Installations	&& Gas detection system outstanding. Works by Gasco.&\\	
\midrule		
4.00	&\textbf{Fire Defense} &&&\\	
4.01	&FHC, FH and Sprinkler Installations	&&Nozzles to be installed. Material issue. Testing of risers. Removal of isolating valve to electrical rooms.&\\	
4.02	&Smoke Exhaust		&&&\\
4.03	&Staircase Pressurization          &&&George to start T\&C\\		
4.04	&Fire Alarm		&& Heat detectors missing. EIs incomplete. Some final fix not complete due to wall papers.&\\
4.05	&FM-200		&&N/A&\\
4.06	&Heliport Foam System	 &&DB heliport not done. Foam installation. Deliveries from Naffco are pending.&\\
4.07   & Emergency lighting &&EI-655 Lvl. 8-48 material not availble HEE responsibility. &Jeffrey\\	
\midrule
5.00	&\textbf{Specialist Services}&&\\

5.01	&Building Management System	&& Commissioning report pending. See chart for BMS per floor.& \\	


5.02	&Security Access Control \& CCTV	&&Installation of battery back-up for access control syste. Material issue. Card readers and push buttons at corridor areas incomplete due to wall paper not completed.&\\	

5.03	&CO Monitoring		&&N/A&\\

5.04	&Car Calling System		&&N/A&\\

5.05	&Lighting Control		&&N/A&\\

5.06	&Structured Cabling		&&To start after podium is ready to avoid damages.& Nidhal\\

5.07	&PA \& Background Music System &&N/A&\\
	
5.08	&IPTV \& Satellite System	&&IPTV System delayed due to late instructions and ordering. Works not started.&\\	

5.09	&Room Management System	&&Status for drawings. RCU terminations not done LVL 18, 19 and 41 VVIP rooms and Presidential suite. No approved termination drawings and RCU components.&Rahul\\

5.10 &Media hub && Not available. Affects all floors.&Nidhal \\

\bottomrule
%\end{tabular}	
\end{longtable}
\end{fullwidth}

\section{EIs}

EI-0012 affecting corridors on Levels 08-17 received 18 Feb 2012. Serious implications.


















