
\cleardoublepage

\chapter*{Update}

Although we are satisfied that the general direction of the Project is doing well, we are currently losing ground on all fronts and we are now behind schedule of about 10 days.

Their a number of reasons for this:

\begin{enumerate}
\item We essentially lost the days due to the Eid holidays. Although we did budget to have personnel to work for at least the two days, due to the general disatisfaction of the labour force - who were instructed to work on Sunday with no overtime benefit. This did cause labour unrest and all days including Thursday were lost.
\item All our subcontractors took the full days off and only returned on Tuesday.
\item Commercial issues on materials are currently result in daily delays. On Rotana 4 days were lost n sourcing minor materials and one-two days were lost in sourcing petty cash.
\item Duct erector shortages continue (despite the addition of more than 35 new personnel from Dubai). Commercial issues with our two major ductwork suppliers took almost 30 days to sort out. 
\end{enumerate}

This report outlines a strategy to be employed in order to complete this Project on time. The deadline of the \protect\deadline  is expected to be met, where no serious constraints exist. The report analyses the strategy to be employed, and sets milestones and expectations. 

It is possible for some of the systems to be commissioned by the deadline. However, proper commissioning and the completion of certain systems, will only be possible after this date. 

Full recovery with the inclusion of additional works being instituted is not possible. A suitable extension of time should be claimed, in order to safeguard HEE and Specon's entitlements and reputation, even if currently HOK is rejecting all claims. 

In Summary, Towers will be substantially completed with false ceiling clearances by mid September and Podia will follow with Testing and Commissioning which are inter-dependent with fit-out installations, and other contractors. Power on will be possible to achieve on Towers Shangri La and Rotana. Merweb will follow, owing to Commercial delays. It is imperative that we appoint an additional subcontractor immediately to help overcome this.
% Start the main matter (normal chapters)

\section*{Recommendations}

Although we are trying our best to continue the works despite the disruptions experienced with the above issues. Decisive steps need to be taken to remedy the situation.

\begin{enumerate}
\item All orders ready to be delivered and pending due to commercial constraints need to be cleared. It will be easier to negotiate terms with Creditors, rather than keep the orders back.

\item Subcontractor payments and VO approvals need to be processed.


\item A decision to stop all works on EIs received after August needs to be taken.

\item Last minute additional resources will be necessary.

\item A larger cash account must be allocated to the Project to eneable procurement of urgent materials that have either been missed or are subject to commercial issues.

\end{enumerate}

