
\cleardoublepage

\chapter*{Executive Summary}

\newthought{Given the current constraints} of the Project, we are satisfied that the general direction of the Project is doing well and we will be in a position to offer the works for Civil Defence Inspection at end of April and shortly thereafter to  handover the buildings to the Operators. 

Physical installations in Towers and Podia have been completed in their majority and final fix activities are following the pace of the Fit-out activities carried out by the Owner's Direct Contractor.  A number of EIs remain to be executed and these are
expected to be completed after the Civil Defence Inspection.

EIs, RFIs and other constraints have slowed down the works and obstructed a reasonable implementation of our original Closure and Commissioning Plan. Commissioning is carried out on works completed

The aim of this report is to summarize the status of the works
and propose a reasonable plan for Closure of the Works and the implementation of a Commissioning Plan.

Below we list milestone dates for substantial completion. Substantial defined as completion of all physical works, excluding certain EIs and works affected by delays due to Owner's Direct Contractors. As for commissioning, our definition of substantial is to complete all activities relating to Civil Defence Inspection. The dates are tight, given the extend of the works, but we are actively working in reducing risks and eliminating constraints.

\begin{longtable}{lll}
\toprule
Item  &Area   & Milestone \\
\midrule
\inc     & Podium Rotana      & 16 Mar 2013\\
\inc     & Tower Rotana       & 16 Mar 2013\\
\inc     & Podium Shangrila  & 16 Mar 2013\\
\inc     & Tower Shangrila    & 28 Mar 2013\\
\inc     & Merweb Podium    & 30 Apr 2013\\
\inc     & Tower Merweb      & 30 Apr 2013\\
\bottomrule
\end{longtable}

\section*{Current Constraints affecting completion}

\begin{enumerate}
\item Continued disruption with EIs and other changes. These EIs will be scheduled for completion after the Civil Defence Inspection (see Tables~\ref{EIsphase3a}\&\ref{EIsphase3b}.
\item Fire Protection (issues with Naffco). Currently we are meeting Naffco regularly and their new management is genuinely trying to solve the issues, however still they are unable to keep to any concrete program.
\item Zeroone resources for data and telephone services (only partly Civil Defence related).
\item Delivery of materials for Fire Alarm. \sidenote{All materials have been ordered and detailed lists are available and being tracked regularly.}
\item Imbalances in resources between the Main Contractor, MEP Subcontractors and Finishing Contractor. This needs to be addressed in order to achieve completion targets.
\end{enumerate}

\section*{Current Action}

The following steps are being implemented to reduce the risks of not achieving the target dates.

\begin{enumerate}
\item  Instituted over-time works for all tradesmen.
\item  Deployment of Electrical Commissioning Manager from HLS UAE to Site. (Already mobilized to Site).
\item  Financial incentive to all subcontractor's to allow for submission of claims every two weeks.
\item  Hiring of additional 20 electricians from ERE.
\item  Deployment of further 50 technicians to be hired from manpower supply companies.
\item  Deployment of a Mechanical Engineer with commissioning skills.
\item  Deployment of one Mechanical Engineer for carrying out smoke tests.\sidenote{This is a time consuming task that needs to be repeated for all the building floors.}
\end{enumerate}


\section*{Personnel}


 Table~\ref{personnel} summarizes the manpower currently on the Project. This is inadequate at the moment to complete the works as planned. We require at least another 30 electricians, 25 duct erectors and 15 plumbers.\sidenote{Electricians are needed for final fix activities, especially for ELV services, duct erectors is mostly supplementary labour for commissioning works on Towers and Podia (duct leakage). Plumbers are needed for Tower rectification works and final fixes.}

\def\Z{\phantom{Z}}
\begin{table}[htbp]
\begin{center}
\begin{tabular}{l r r}
\toprule
Company           &Tradesmen  \\
~                 &25 Feb \\
\midrule
HLS                &219         \\
Al-Jaber          &34         \\
Crompton        &20           \\
QMMC            &16        \\
Nafco             &9           \\
ERE (subcontract)               &10          \\
                 
                  &\underline{\phantom{1075}}\\
Subtotal          &\textbf{287}        \\

Hired manpower    &         \\
\Z ERE            &21        \\
          
                 
&&\\
Total                      &\textbf{308}       \\
                           
\bottomrule
\end{tabular}
\caption{Average Manpower as of January 2013}
\label{personnel}
\end{center}
\end{table}





\section*{EI Management}
\input{./Sections/EI-status}

\section*{Detailed Action Plan}

In the sections that follow we describe the detailed methodology and status of works for each individual service. \tref{masterplan} shows the current status of Testing \& Commissioning.

\input{./Sections/listofservices-plan}

\section*{Conclusions}

We have outlined a plan that we are confident we can meet from our end. We are hoping that all parties involved can continue their co-operation with HLG \& HLS to remove existing constraints and or new issues that may arise during finalization to bring the Project to a successful conclusion. We also hope that the Direct Owner's Contractors can increase their pace of works to enable us to complete works without any further delays.



